---
title: "Student Success Dashboard Template"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
#runtime: shiny
---

```{r setup, include=FALSE,echo=FALSE}
# Set up the document and configure code chunk options
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Load required R packages using 'pacman'
if(require(pacman) == FALSE) install.packages("pacman")
pacman::p_load(
  tidyverse,      # Data manipulation and visualization
  plotly,         # Interactive plots
  flexdashboard,  # Dashboard creation
  fontawesome,    # For icons
  DT,             # Enhanced tables
  dplyr,
  gridExtra
)

# Read in the data from "clean_data.rds"
cd = readRDS("clean_data.rds")
```

# Project Overview


### **Data Overview**

- Annually, the FSB conducts a senior survey of graduates to learn about their employment status.
- Information is verified using LinkedIn and employer survey data.
- The provided data ('FSB_BI_Survey_2019_2021.rds') includes graduates' information from 2019, 2020, and 2021.
- The data is merged from two sources: the senior survey and the Miami University database.
- The dataset underwent extensive cleaning and preparation to focus on relevant data points.

### **Project Goals**

- Determine the correlation between student internships and job placement at the Farmer School of Business.
- Utilize data from Mr. Kirk Bogard to conduct graphical analysis for insights.
- Create visualizations to help students, career services staff, and prospective donors understand the impact of internships on post-graduate job placement.
- Primary goals:
  - Analyze the relationship between internships and post-grad job placement.
  - Communicate the results in an easily understandable format to convey the findings accurately.

### **Insights**

- **Internship Connection with Job Placement:**
  - The majority of students (1966 out of 2182 students) had at least one internship during their college career.
  - Of those 1966 students, 1649 received at least one job offer.
  - Even among the students without internships, 107 of them received a job offer, while 109 didn't.
- **Key Findings:**
  - Most FSB students have internships during their undergraduate studies.
  - Students with internships have a significantly higher likelihood of receiving job offers.
- **Data Exploration:**
  - This dashboard explores the relationship between internships and job offers.
  - Additionally, it delves into how these variables affect different majors.
  - Similar trends are observed across all majors.


# Survey Overview {data-orientation="columns"}

Overview of survey responses

## row {data-width="300"}

### Usable Response Rate

```{r, echo = FALSE}
rate=round(100*nrow(cd)/3235,0) #used records vs records in original data
gauge(rate, min=0,max=100,symbol='%',gaugeSectors(success=c(80,100),warning=c(40,79),danger = c(0,39)))
```

### Usable Responses

```{r,echo=FALSE}
nusable=nrow(cd) #used records represented numerically
valueBox(nusable,icon="fa-users")
```

### Internship Count

```{r,echo=FALSE}
#number of students with each number of internships
p=ggplot(cd,aes(survey_internships))+
  geom_bar(color="steelblue",fill="steelblue")+
  xlab("Number of Internships")+
  ylab("Number of Responses")+
  theme_bw()
ggplotly(p)
```

## row {data-height="600"}

### Internship Rate by Primary Major

```{r,echo=FALSE}
#% of each major with at least one internship
internships_by_major <- cd %>%
  mutate(at_least_one_internship = ifelse(survey_internships > 0, 1, 0))

internship_rate <- internships_by_major %>%
  group_by(major1) %>%
  summarize(internship_rate = mean(at_least_one_internship))

p <- ggplot(internship_rate, aes(x = major1, y = internship_rate)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Internship Rate by Major",
       x = "Major",
       y = "Internship Rate") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggplotly(p)
```

### Offer Rate by Primary Major

```{r,echo=FALSE}
#% of each major with at least one job offer
offers_by_major <- cd %>%
  mutate(at_least_one_offer = ifelse(survey_offers > 0, 1, 0))

offer_rate <- offers_by_major %>%
  group_by(major1) %>%
  summarize(offer_rate = mean(at_least_one_offer))

p = ggplot(offer_rate, aes(x = major1, y = offer_rate)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  labs(title = "Offer Rate by Major",
       x = "Major",
       y = "Offer Rate") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggplotly(p)
```

# Analysis Results {data-orientation="columns"}

## Column {data-width="400"}

### Job Offer Counts vs Internship Status

```{r,echo=FALSE}
#job offer rate for students with internships vs those without (most important graph)
cd$internship_status <- ifelse(cd$survey_internships > 0, "Had Internship", "Zero Internships")
cd$job_offer_status <- ifelse(cd$survey_offers > 0, "Received Offer", "Zero Offers")
# Reorder the levels of the "job_offer_status" factor
cd$job_offer_status <- factor(cd$job_offer_status, levels = c("Zero Offers", "Received Offer"))

# Create the bar chart
bar_chart <- ggplot(cd, aes(x = internship_status, fill = job_offer_status)) +
  geom_bar(position = "dodge") +
  labs(title = "Job Offers vs. Internships",
       x = "Internship Status",
       y = "Number of Students") +
  scale_fill_manual(values = c("Received Offer" = "steelblue", "Zero Offers" = "red"))

ggplotly(bar_chart)
```

### Job Offer Counts

```{r,echo=FALSE}
#number of students receiving each number of job offers
job_offers_plot <- cd %>%
  ggplot(aes(x = reorder(as.character(survey_offers), as.numeric(survey_offers)))) +
  geom_bar(fill = "steelblue", color = "steelblue") +
  labs(title = "Job Offers Count",
       x = "Number of Job Offers",
       y = "Number of Students")

# Convert the ggplot to an interactive plot
job_offers_plotly <- ggplotly(job_offers_plot)

job_offers_plotly

```

## Column {data-width="600"}

### Job Offers vs Internships by Major

```{r,echo=FALSE}
#job offer status by number of internships and major
cd$offer_status <- ifelse(cd$survey_offers > 0, "Received Offer", "No Offer")

# Create the clustered bar plot with facet_wrap
p <- ggplot(cd, aes(x = factor(survey_internships), fill = offer_status)) +
  geom_bar(position = "dodge") +
  labs(title = "Job Offers vs. Internships by Major",
       x = "Number of Internships",
       y = "Number of Students") +
  facet_wrap(~ major1, ncol = 2) +
  scale_fill_manual(values = c("Received Offer" = "steelblue", "No Offer" = "red"))

# Convert the ggplot to an interactive plot
ggplotly(p)
```

# Session Info
```{r}
sessionInfo()
```

